%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\usepackage{enumerate}
\name{Qinglin Li} % Your name
\address{1915 Maple Avenue, APT 910-A, Evanston, IL, 60201} % Your address
\address{Github: \href{github.com/lostleaf}{github.com/lostleaf}}
\address{+1 (847) 246-2457 \\ \href{mailto:qinglinli2015@u.northwestern.edu}{qinglinli2015@u.northwestern.edu}}



\begin{document}
%\begin{rSection}{Objective}
%I'm looking for a 2016 summer internship in software development or data science related area.
%\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace{10pt}

\begin{rSection}{Education}
\begin{rSubsection}{Northwestern University}{SEP 2015 - DEC 2016 (Expected)}{Chicago, USA\quad GPA:  \textsc{4.0/4.0}}\\
M.S. in Computer Science
%Coursework: Machine Learning, Biometrics, Data Science, Computer Vision, Geospatial Vision and Visualization, CUDA programming, Human Computer Interaction
\end{rSubsection}
\vspace{5pt}
\begin{rSubsection}{Shanghai Jiao Tong University}{SEP 2011 - JUN 2015}{Shanghai, China\quad GPA:  \textsc{3.5/4.0}}\\
B.S. in Computer Science \& Engineering
%Coursework: Statistical Learning, Scientific Computing, Algorithms,  Operating System, Computer Network, Database, Computer Architecture, etc.
\end{rSubsection}
\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\vspace{10pt}

\begin{rSection}{Experience}
\begin{rSubsection}{Computer Vision Engineer Intern}{JUN 2016 - SEP 2016}{}
	
	{\em HERE North America LLC \hfill Chicago, USA}
	
	%Team: Natural Language Computing, Mentor: Dr. Mu Li
	\begin{itemize}
	\item Trained a deep convolutional neural network(fully convolutional encoder-decoder structure) for lane detection with Caffe. This model could detect most of the lane lines when tested with street view images on highways.
	\item Created wrappers for Caffe Deep Learning training and testing automation in Python.
	\item Implemented a tool for LiDAR point cloud colorization with street view images in C++, OpenCV and GeographicLib.
	\item Cooperated with other team members to QA the road geometry generated from the LiDAR high definition map pipeline.
	\end{itemize}
\end{rSubsection}	

\begin{rSubsection}{Research Intern}{AUG 2014 - FEB 2015}{}

{\em Microsoft Research Asia \hfill Beijing, China}

%Team: Natural Language Computing, Mentor: Dr. Mu Li
\begin{itemize}
\item Research on the knowledge bases entities English-Chinese translation problem with Natural Language Processing team and implemented a graphical model with Python and Numpy. Compared to a SVM baseline, accuracy is improved from 50\% to 90\% when tested on a movie knowledge base.
\item Wrote crawlers to collect and analyze English-Chinese translations from Internet in Python.
\end{itemize}
\end{rSubsection}
\vspace{5pt}
\begin{rSubsection}{Research Assistant}{JUL 2013 - AUG 2014}{}
	
{\em BCMI Lab of Shanghai Jiao Tong University \hfill Shanghai, China}

%Research Area: Computer Vision, Mentor: Prof. Liqing Zhang
\begin{itemize}
\item Researched on feature engineering of the crow density estimation problem and proposed a easy to train method combining a rich bank of low level image features and non linear support vector regression reached state-of-the-art performance. This work is then selected as a Shanghai College Student Innovation Practice Project.
\end{itemize}
\end{rSubsection}
\begin{rSubsection}{Team leader}{SEP 2015 - NOV 2015}{}
	
	{\em CoolWildCats ACM-ICPC team of Northwestern University \hfill Chicago, USA}
	

	\begin{itemize}
		\item Leaded the CoolWildCats team, representing Northwestern University, won the 4th place in 2015 ACM-ICPC Mid-Central USA Regional contest.
	\end{itemize}
\end{rSubsection}
\end{rSection}

%\vspace{10pt}

\begin{rSection}{Skills}
	Years of experience in Computer Vision(OpenCV) and Machine Learning \\
	Proficient in C++ and Python \\
	Working Experience in Deep Learning frameworks Caffe, Tensorflow and MXNet \\
	Experience in Java, Ruby, MATLAB, Linux commands and tools such as Vim and Git \\ 
	Knowledge of Web development skills including HTML, CSS, JavaScript, Ruby on Rails and MySQL
	
\end{rSection}
%----------------------------------------------------------------------------------------
%	COURSE PROJECT EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
%\vspace{10pt}

%\begin{rSection}{Projects}%{\begin{bf}GitHub\end{bf}: \href{https://github.com/lostleaf?tab=repositories}{https://github.com/lostleaf}}
%
%\begin{rSubsection}{Fatworm Database System}{FALL 2014}{Shanghai Jiao Tong University}
%\begin{itemize}
%\item Developed a relational database system supporting JDBC interface including SQL parser, query engine and file storage in Java.
%\end{itemize}
%\end{rSubsection}
%\vspace{3pt}
%\begin{rSubsection}{Nachos Operating System}{FALL 2013}{Shanghai Jiao Tong University}
%\begin{itemize}
%\item Implemented threading and multiprogramming, virtual memory, and a self-designed file system within the Nachos operating system in Java.
%\end{itemize}
%\end{rSubsection}
%\vspace{3pt}
%\begin{rSubsection}{C Language Compiler}{SPRING 2013}{Shanghai Jiao Tong University}
%\begin{itemize}
%\item Developed a compiler of the C Language targeting the MIPS architecture including parser, syntax checking and the linear scan algorithm for register allocation in Java.
%\end{itemize}
%\end{rSubsection}
%\vspace{3pt}
%\begin{rSubsection}{Simulated CPU}{SPRING 2013}{Shanghai Jiao Tong University}
%\begin{itemize}
%\item Simulated a CPU with Tomasula algorithm for dynamic instruction scheduling in Verilog.
%\end{itemize}
%\end{rSubsection}
%
%\end{rSection}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

%\vspace{10pt}
\begin{rSection}{Services}
\textbf{Coach} of Rails Girls Beijing \hfill 2014\\
\textbf{Teaching Assistant} for the C++ programming course at Shanghai Jiao Tong University \hfill 2013\\
\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}